\section*{Acknowledgements}
All praise goes to the Almighty Allah, for giving us the ability and potential to finish
our project. We are sincerely grateful to our supervising teacher, Prof. Shilpi Akter (Dean, Faculty of Textile Engineering; Professor, Department of Fabric Engineering), for her excellent support and guidance. From the first hour to the end of our project, she has provided us with guidance, continuous motivation, and time saving advice, all of which have guided us towards fulfilling our project. She also shared her experience of her project which guide us towards the points that we need to work on. We are truly grateful for her support and direction throughout this project. We would like to express our heartfelt appreciation to the industrial personnel involved in the shredding and recycling of waste textiles. Their contribution played a vital role in supporting our project by providing us with the necessary shredded and chopped textile waste entirely free of cost. Our final appreciation also goes to Md. Mansoor Alam (Chemical supplier) for his timely and efficient delivery of the essential chemicals required for our project. His prompt service played a crucial role in ensuring that our work progressed without any delays. In addition to the timely supply, he also extended valuable support by providing detailed safety guidance regarding the handling and usage of the chemicals. He clearly identified which substances were hazardous and instructed us on the appropriate precautions to take during storage, usage, and disposal. We would like to extend our sincere thanks to the Mr. Azizul Haque; owner of Furniture Mart, Jamalpur who provided us with the required die for our project work. The die was delivered on time and crafted precisely to the specifications we had shared, ensuring a smooth and efficient workflow. In addition to delivering the die with the correct shape and dimensions, and also offered valuable guidance on its usage.