\section{Application and End Use}

% --------------- 4.5.1 --------------------%
\subsection{Epoxy Composite Brick}
Due to their moderate compressive strength, they are well-suited for moisture-resistant applications. Their durability and resilience make them ideal for decorative features and eco-friendly construction. \\

\noindent Application Areas:
\begin{enumerate}
	\item Non-load bearing walls.
	\item Industrial flooring \& wall-base.
	\item Protective enclosure.
	\item Moisture prone Areas (Kitchens, Bathrooms).
	\item External facade panels.
	\item Decorative features (Accent Walls, Panels).
	\item Sustainable construction (Green building).
\end{enumerate}

% --------------- 4.5.2 --------------------%
\subsection{Polyester Composite Brick}
Polyester bricks, which are created by mixing shredded textile waste with polyester resin and hardeners, which are more powerful than epoxy bricks. Their superior compressive strength them appropriate for load-bearing uses. Polyester bricks are especially suitable for prefabricated and modular home solutions. \\

\noindent Application Areas:
\begin{enumerate}
	\item Non-load bearing / Partition walls.
	\item Boundary \& Compound walls.
	\item Facade cladding.
	\item Pavement \& footpath construction.
	\item Prefabricated and modular housing.
	\item Sustainable construction (Eco-friendly projects).
\end{enumerate}

% --------------- 4.5.3 --------------------%
\subsection{Plaster of Paris (POP) Composite Brick}
Plaster of Paris bricks are non-load-bearing, lightweight materials that are manufactured by blending shredded textile waste with POP and cement. Since they possess poor compressive strength, they are used mostly for decorative and temporary purposes in construction. \\

\noindent Application Areas:
\begin{enumerate}
	\item Patterned/Decorative interior walls.
	\item Decorative false ceilings.
	\item Exhibition booths, Display stands.
	\item Low height edging, border in gardens or parks.
	\item Carving for ornamental detailing.
	\item Sustainable construction.
\end{enumerate}