\chapter{Result and Discussion}
This chapter discusses and presents the comprehensive performance testing of the newly developed composite bricks fabricated using shredded textile waste integrated with various binder systems. In an effort to promote sustainable and eco-friendly construction materials, three distinct formulations were designed. Each formulation contained an identical quantity of chopped textile waste (100 grams), which was uniformly mixed with different types of binders to evaluate their influence on brick properties.  The first formulation utilized epoxy resin and hardener, known for their excellent bonding and mechanical strength. \\

\noindent The second composition included polyethylene terephthalate (PET) resin along with appropriate catalysts, selected for its thermoplastic characteristics and chemical resistance. The third mixture employed a plaster of Paris (POP) and cement blend, offering a more conventional and cost-effective alternative. \\

\noindent All composite mixtures were thoroughly blended and cast in a standardized rectangular brick mold with dimensions of 200 mm $\times$ 100 mm $\times$ 60 mm. After proper curing, the fabricated bricks underwent a series of standardized tests to evaluate their mechanical and physical properties.  \\

\noindent These tests included compressive strength, surface hardness, flexural strength, water absorption, and density, conducted in accordance with relevant ASTM standards. The primary objective of this testing phase was to assess the structural viability, durability, and potential application of these textile-reinforced composite bricks in real-world construction scenarios. \\

\noindent Through this comparative evaluation, insights were gained regarding the most suitable binder for enhancing the mechanical performance and sustainability of textile waste based bricks.

\input{Sections/4.1}
\input{Sections/4.2}
\input{Sections/4.3}
\input{Sections/4.4}
\input{Sections/4.5}